\begin{conf-abstract}
{Quantifying Carbon Cycling across the Groundwater-Stream-Atmosphere Continuum Using High-Resolution Time Series of Multiple Dissolved Gases}
{Chuan Wang}
{Eawag, Swiss Federal Institute of Aquatic Science and Technology}
{The quantification of carbon cycling across the groundwater-stream-atmosphere
continuum (GSAC) is crucial for understanding regional and global carbon cycling. However, this
quantification remains challenging due to highly coupled carbon exchange and turnover in the GSAC.
Here, we disentangled carbon cycling processes in a representative groundwater-stream-atmosphere
transect by obtaining and numerically simulating high-resolution time series of dissolved He, Ar, Kr,
O2, CO2, and CH4 concentrations. The results revealed that groundwater contributed $\sim$60\% of CO2
and $\sim$30\% of CH4 inputs to the stream, supporting stream CO2 and CH4 emissions to the atmosphere.
Furthermore, diurnal variations in stream metabolism (-0.6 to 0.6 mol O2 m-2 day-1) induced
pronounced carbonate precipitation during the day and dissolution at night. The significant diurnal
variability of biogeochemical processes emphasizes the importance of high-resolution time series
investigations of carbon dynamics. This study shows that dissolved gases are promising environmental
tracers for discerning and quantifying carbon cycling across the GSAC with high spatiotemporal
resolution. Our high-resolution carbon exchange and turnover quantification provides a processoriented
and mechanistic understanding of carbon cycling across the GSAC.}
\end{conf-abstract}
